---
title: "rSocialWatcher"
#author: "Robert Marty"
#date: "`r Sys.Date()`"
#output: rmarkdown::html_vignette
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{rSocialWatcher}
  %\VignetteEncoding{UTF-8}
#vignette: >
#  %\VignetteEngine{knitr::knitr}
#  %\VignetteIndexEntry{Title of your vignette}
#  %\usepackage[UTF-8]{inputenc}
#vignette: >
#  %\VignetteIndexEntry{Vignette Title}
#  %\VignetteEngine{knitr::rmarkdown}
#  %\VignetteEncoding{UTF-8}
---



```{r init, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Setup <a name="setup"></a>

First, we load relevant packages and create variables for our Facebook API keys.

```{r setup, include=TRUE, warning=FALSE, message=FALSE}
## Load Google Traffic package
library(rSocialWatcher)

## Load packages for working with and visualizing data
library(tidyverse)

library(dplyr)
library(lubridate)
library(jsonlite)
library(httr)
library(stringr)

library(knitr)
library(kableExtra)

## Set Facebook Keys
TOKEN        <- "TOKEN-HERE"
CREATION_ACT <- "CREATION-ACT-HERE"
VERSION      <- "VERSION-HERE"
```

```{r loadkey, include=FALSE}
## Load keys
api_keys <- read.csv("~/Dropbox/World Bank/Webscraping/Files for Server/api_keys.csv",
                     stringsAsFactors = F)

api_keys <- api_keys %>%
  dplyr::filter(Service == "facebook_marketing_ad",
                Details == "robmarty3@gmail.com")

TOKEN <- api_keys %>% 
  dplyr::filter(Account == "token") %>% 
  pull(Key)

CREATION_ACT <- api_keys %>% 
  dplyr::filter(Account == "creation_act") %>% 
  pull(Key) %>% 
  str_replace_all("ACT_", "") 

VERSION <- api_keys %>% 
  dplyr::filter(Account == "version") %>% 
  pull(Key)
```

---

# Querying Parameter IDs <a name="query_param"></a>

## Demographics, Interests, & Behaviors <a name="param_dib"></a>

```{r simple_dib_ex, include=TRUE, warning=FALSE, message=FALSE}
behaviors_df <- get_fb_parameter_ids(type    = "behaviors",
                                     version = VERSION, 
                                     token   = TOKEN)

demographics_df <- get_fb_parameter_ids(type    = "demographics",
                                        version = VERSION, 
                                        token   = TOKEN)

interests_df <- get_fb_parameter_ids(type    = "interests",
                                     version = VERSION, 
                                     token   = TOKEN)

behaviors_df %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%",
             height = "300px")
```

## Location IDs <a name="param_locs"></a>

```{r simple_loc_ex, include=TRUE, warning=FALSE, message=FALSE}
country_df <- get_fb_parameter_ids(type    = "country",
                                   version = VERSION, 
                                   token   = TOKEN)

country_group_df <- get_fb_parameter_ids(type    = "country_group",
                                         version = VERSION, 
                                         token   = TOKEN)

us_states_df <- get_fb_parameter_ids(type    = "region",
                                     version = VERSION, 
                                     token   = TOKEN,
                                     country_code = "US")

ny_key <- us_states_df %>% filter(name == "New York") %>% pull(key) 
ny_cities_df <- get_fb_parameter_ids(type    = "city",
                                     version = VERSION, 
                                     token   = TOKEN,
                                     region_id = ny_key,
                                     q = "New York")

country_df %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%",
             height = "300px")
```

# Querying Data <a name="query_data"></a>

## Different Location Types <a name="query_data_loc"></a>

### Radius around lat/lon <a name="query_data_loc_latlon"></a>

```{r simple_query_latlon_ex, include=TRUE, warning=FALSE, message=FALSE}

## All Facebook Users by Radius (Near NYC)
r5km_df <- query_fb_marketing_api(location_unit_type = "coordinates",
                                  lat_lon = c(40.712, -74.006),
                                  radius = 5,
                                  radius_unit = "kilometer",
                                  version            = VERSION, 
                                  creation_act       = CREATION_ACT, 
                                  token              = TOKEN)
```

### Location IDs - Country, State, District, City, Neighborhood, etc. <a name="query_data_loc_keys"></a>

We can also query using different location types, including countries, cities, etc. The `get_fb_parameter_ids()` function can be used to extract location keys for different location types; the location keys can then be used in the `query_fb_marketing_api()`. The below table indicates all the location types supported by the package. 

* __Location Type:__ This is specified (1) in the `type` parameter in the `get_fb_parameter_ids()` function and in the `location_unit_type` parameter in the `query_fb_marketing_api()` function
* __Radius Can be Specified:__ For these location types, a radius can optionally be specified; for example, to specify a location and it's surrounding area.
* __US Only:__ These location types can only be used for the US

| Location Type      | Radius Can be Specified | US Only |
| -----------------  | ----------------------  | ------- |
| country_group      | No                      | No      |
| country            | No
| region             |
| large_geo_area     |
| medium_geo_area    |
| small_geo_area     |
| metro_area         |
| city               |
| subcity            |
| neighborhood       |
| subneighborhood    |
| zip                |
| geo_market         |
| electoral_district |

```{r simple_query_lockey_ex, include=TRUE, warning=FALSE, message=FALSE}

## All Facebook Users by Radius (Near NYC)
r5km_df <- query_fb_marketing_api(location_unit_type = "coordinates",
                                  lat_lon = c(40.712, -74.006),
                                  radius = 5,
                                  radius_unit = "kilometer",
                                  version            = VERSION, 
                                  creation_act       = CREATION_ACT, 
                                  token              = TOKEN)

## All Facebook Users within US
us_df <- query_fb_marketing_api(location_unit_type = "countries",
                                location_keys      = "US",
                                version            = VERSION, 
                                creation_act       = CREATION_ACT, 
                                token              = TOKEN)

## All Facebook Users within NYC
nyc_key <- ny_cities_df %>% filter(name == "New York") %>% pull(key)
nyc_df <- query_fb_marketing_api(location_unit_type = "cities",
                                 location_keys      = nyc_key,
                                 version            = VERSION, 
                                 creation_act       = CREATION_ACT, 
                                 token              = TOKEN)

nyc_df %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%",
             height = "300px")

```

## ID Options <a name="query_data_ids"></a>

### Options <a name="query_data_ids_options"></a>

```{r simple_query_params_ex, include=TRUE, warning=FALSE, message=FALSE}

# Likely commute to work in US
beh_comm_id <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
comm_us_df <- query_fb_marketing_api(location_unit_type = "countries",
                                     location_keys      = "US",
                                     behaviors          = beh_comm_id,
                                     version            = VERSION, 
                                     creation_act       = CREATION_ACT, 
                                     token              = TOKEN)

# Interested in music in US
int_music_id <- interests_df %>% filter(name == "Music (entertainment & media)") %>% pull(id)
music_us_df <- query_fb_marketing_api(location_unit_type = "countries",
                                      location_keys      = "US",
                                      interests          = int_music_id,
                                      version            = VERSION, 
                                      creation_act       = CREATION_ACT, 
                                      token              = TOKEN)

# Likely commute to work OR interested in music in US
comm_or_music_us_df <- query_fb_marketing_api(location_unit_type = "countries",
                                              location_keys      = "US",
                                              behaviors          = beh_comm_id,
                                              interests          = int_music_id,
                                              version            = VERSION, 
                                              creation_act       = CREATION_ACT, 
                                              token              = TOKEN)
```

### And and OR Categories <a name="query_data_ids_andor"></a>

When using multiple parameters (eg, behavior IDs), the function allows for specifying `and` and `or` condition; for example, identifying Facebook users that are commuters and/or are frequent travelers. Across parameters:

* __Vectors `c()`__ are used to specify OR conditions
* __Lists `list()`__ are used to specify AND conditions

However, the following parameters can only except one input (a list or vector is not allowed).
* `location_unit_type`
* `radius`
* `radius_unit`

#### Within parameter types <a name="query_data_ids_andor_within"></a>

```{r and_or_within, include=TRUE, warning=FALSE, message=FALSE}

beh_freqtrvl_id  <- behaviors_df %>% filter(name == "Frequent Travelers") %>% pull(id)
beh_comm_id      <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
beh_sb_id        <- behaviors_df %>% filter(name == "Small business owners") %>% pull(id)

# Commuters or Travelers
comm_or_trvl_df <- query_fb_marketing_api(location_unit_type = "countries",
                                          location_keys      = "US",
                                          behaviors          = c(beh_comm_id, beh_freqtrvl_id),
                                          version            = VERSION, 
                                          creation_act       = CREATION_ACT, 
                                          token              = TOKEN)

# Users who are (Commuters or Small Business Owners) and Travelers
comm_and_trvl_df <- query_fb_marketing_api(location_unit_type = "countries",
                                           location_keys      = "US",
                                           behaviors          = list(c(beh_comm_id,
                                                                       beh_sb_id), 
                                                                     beh_freqtrvl_id),
                                           version            = VERSION, 
                                           creation_act       = CREATION_ACT, 
                                           token              = TOKEN)
```

#### Flexible Targetting: Or and And <a name="query_data_ids_andor_flex"></a>

Flexible tagetting, using the `flex_target` parameter, allows for more complicated parameter specification---including AND conditions across parameter types (eg, behavior X and interest Y). The input for `flex_target` follows the following logic:

* `flex_target` uses named lists to specify the (1) parameter type and (2) parameter ID
* All parameters within the same list index are grouped using an OR condition
* All parameter separated across list indices are spearated by an AND condition

The below shows examples using dummy IDs

__Example 1: OR Condition__
The below shows an example setting an OR condition for interest ID 2 and behavior ID 2. Both interest:1 and behavior:2 are in the same list index, so are grouped using an OR condition (interests:1 OR behavior 2)
```
flex_param <- list("interests" = 1, "behaviors" = 2)
# flex_param[[1]]
```

__Example 2: AND Condition__
The below shows an example setting an AND condition for interest ID 2 and behavior ID 2. interest:1 and behavior:2 are separated across list indices, so are separated by an AND condition (interests:1 AND behavior:2)
```
flex_param <- list(list("interests" = 1), list("behaviors" = 2))
# flex_param[[1]] AND flex_param[[2]]
```

__Example 3: OR and AND Conditions__
The below shows a more complicated example, which grabs all users that meet EITHER interests:1 or behaviors:3 AND behaviors:2. Everything within `flex_param[[1]]` are grouped within OR conditions, but different indices (`flex_param[[1]]` and `flex_param[[2]]`) are separated by AND conditions.
```
flex_param <- list(list("interests" = 1, "behaviors" = 3), list("behaviors" = 2))
# flex_param[[1]] AND flex_param[[2]]
```

```{r and_or_across, include=TRUE, warning=FALSE, message=FALSE}

int_music_id <- interests_df %>% filter(name == "Music (entertainment & media)") %>% pull(id)
beh_comm_id  <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)

## OR CONDITION
comm_or_music_df <- query_fb_marketing_api(location_unit_type = "countries",
                                           location_keys      = "US",
                                           flex_target        = list("interests" = int_music_id,
                                                                     "behaviors" = beh_comm_id),
                                           version            = VERSION, 
                                           creation_act       = CREATION_ACT, 
                                           token              = TOKEN)

## AND CONDITION
comm_and_music_df <- query_fb_marketing_api(location_unit_type = "countries",
                                            location_keys      = "US",
                                            flex_target        = list(list("interests" = int_music_id),
                                                                      list("behaviors" = beh_comm_id)),
                                            version            = VERSION, 
                                            creation_act       = CREATION_ACT, 
                                            token              = TOKEN)

```

### Exlcuding Categories <a name="query_data_ids_exclude"></a>

Many parameters come with an alternate input that starts with `excl_` to exclude types of users. For example, there are both `behaviors` and `interests` parameters, as well as `excl_behaviors` and `excl_interests` parameters. The below code shows an example querying users who likely commute to work and are not tagged as interested in music.

```{r exclude_ex, include=TRUE, warning=FALSE, message=FALSE}

# Likely commute to work BUT NOT interested in music in US
beh_comm_id  <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
int_music_id <- interests_df %>% filter(name == "Music (entertainment & media)") %>% pull(id)

comm_no_music_us_df <- query_fb_marketing_api(location_unit_type = "countries",
                                              location_keys      = "US",
                                              behaviors          = beh_comm_id,
                                              excl_interests     = int_music_id,
                                              version            = VERSION, 
                                              creation_act       = CREATION_ACT, 
                                              token              = TOKEN)
```


## Multiple Queries <a name="query_data_ids_multquery"></a>

The function allows making multiple queries within one function call. All parameters in the `map_param` function will be iterated as separate calls

### Simple Examples <a name="query_data_ids_multquery_simple"></a>

```{r vec_list_1, include=TRUE, warning=FALSE, message=FALSE}
## Number of Users in US or Mexico, as separate queries
df_out <- query_fb_marketing_api(location_unit_type = "countries",
                                 location_key       = map_param("US", "MX"),
                                 version            = VERSION, 
                                 creation_act       = CREATION_ACT, 
                                 token              = TOKEN)

df_out %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")

## Iterate across countries and across behaviors. Use `NA` for not filtering by behavior. The below call will give users for (1) all US, (2) all Mexico, (3) frequent travelers in US, and (4) frequenty travelers in Mexico.
df_out <- query_fb_marketing_api(location_unit_type = "countries",
                                 location_key       = map_param("US", "MX"),
                                 behaviors          = map_param(NA, beh_freqtrvl_id),
                                 version            = VERSION, 
                                 creation_act       = CREATION_ACT, 
                                 token              = TOKEN)

df_out %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")

## Separate query for number of users in US and Mexico and commuters and frequent travelers. Parameters not in
## map_param are applied across all queries. 
beh_comm_id      <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
beh_freqtrvl_id  <- behaviors_df %>% filter(name == "Frequent Travelers") %>% pull(id)
beh_sb_id        <- behaviors_df %>% filter(name == "Small business owners") %>% pull(id)
int_music_id     <- interests_df %>% filter(name == "Music (entertainment & media)") %>% pull(id)

df_out <- query_fb_marketing_api(location_unit_type = "countries",
                                 location_key       = map_param("US", "MX"),
                                 behaviors          = map_param(beh_comm_id, beh_freqtrvl_id),
                                 interests          = int_music_id,
                                 version            = VERSION, 
                                 creation_act       = CREATION_ACT, 
                                 token              = TOKEN)

df_out %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")
```

### And/Or Conditions <a name="query_data_ids_multquery_andor"></a>

And/or conditions work as before: vectors `c()` specify OR conditions, while lists `list()` specify and conditions

```{r vec_list_1_andor, include=TRUE, warning=FALSE, message=FALSE}

beh_freqtrvl_id  <- behaviors_df %>% filter(name == "Frequent Travelers") %>% pull(id)
beh_comm_id      <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
beh_sb_id        <- behaviors_df %>% filter(name == "Small business owners") %>% pull(id)

df_out <- query_fb_marketing_api(location_unit_type = "countries",
                                 location_key       = "US",
                                 behaviors          = map_param(
                                   # Commuters
                                   beh_comm_id, 
                                   
                                   # Frequent Travelers
                                   beh_freqtrvl_id, 
                                   
                                   # Commuters OR Frequent Travelers
                                   c(beh_comm_id, beh_freqtrvl_id),
                                   
                                   # Commuters AND Frequent Travelers
                                   list(beh_comm_id, beh_freqtrvl_id),
                                   
                                   # Commuters AND (Frequent Travelers OR Small Business Owners)
                                   list(beh_comm_id, c(beh_freqtrvl_id, beh_sb_id))
                                 ),
                                 
                                 version            = VERSION, 
                                 creation_act       = CREATION_ACT, 
                                 token              = TOKEN)

df_out %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")
```
