---
title: "rSocialWatcher"
#author: "Robert Marty"
#date: "`r Sys.Date()`"
#output: rmarkdown::html_vignette
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{rSocialWatcher}
  %\VignetteEncoding{UTF-8}
---

```{r init, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Setup <a name="setup"></a>

First, we load relevant packages and create variables for our Facebook API keys.

```{r setup, include=TRUE, warning=FALSE, message=FALSE}
## Load Google Traffic package
library(rSocialWatcher)

## Load packages for working with and visualizing data
library(tidyverse)

library(dplyr)
library(lubridate)
library(jsonlite)
library(httr)
library(stringr)

library(knitr)
library(kableExtra)

## Set Facebook Keys
TOKEN        <- "TOKEN-HERE"
CREATION_ACT <- "CREATION-ACT-HERE"
VERSION      <- "VERSION-HERE"
```

```{r loadkey, include=FALSE}
## Load keys
api_keys <- read.csv("~/Dropbox/World Bank/Webscraping/Files for Server/api_keys.csv",
                     stringsAsFactors = F)

api_keys <- api_keys %>%
  dplyr::filter(Service == "facebook_marketing_ad",
                Details == "robmarty3@gmail.com")

TOKEN <- api_keys %>% 
  dplyr::filter(Account == "token") %>% 
  pull(Key)

CREATION_ACT <- api_keys %>% 
  dplyr::filter(Account == "creation_act") %>% 
  pull(Key) %>% 
  str_replace_all("ACT_", "") 

VERSION <- api_keys %>% 
  dplyr::filter(Account == "version") %>% 
  pull(Key)
```

---

The `rSocialWatcher` package provides two functions:

* `get_fb_parameter_ids`: To obtain IDs for targeting users by different characteristics, including different types and by their location.
* `query_fb_marketing_api`: Query daily and monthly active users, querying users for specific locations and by specific types. 

# Querying Parameter IDs <a name="query_param"></a>

The `get_fb_parameter_ids` function facilitates querying IDs to target specific types of users (e.g., users with specific interests) and to target users in specific locations (eg, countries, cities, etc).

## User Type IDs <a name="param_users"></a>

Targeting specific types of users can be done along a number of categories, including by users' interests, behaviors, job, etc. Using the `get_fb_parameter_ids` function, the `type` parameter is used to query IDs for different types of categories. The `type` parameter allows for the following inputs: 

* __behaviors__
* __demographics__
* __interests__
* __industries__
* __life_events__
* __family_statuses__
* __education_statuses__
* __relationship_statuses__
* __education_major__
* __income__ Only available for using in the United States
* __job_titles__ When setting `type = "job_titles"`, the `q` parameter is also required. The `q` parameter restricts the search by names. Consequently, setting `q = "data"` will query job titles with "data" in the name, such as "Database Engineer" and "Data Analyst."

IDs can then be used in the `query_fb_marketing_api` function, which queries daily and monthly active Facebook users. For each `type` input, there is a parameter in the `query_fb_marketing_api` function to include the ID for the specific type. For example, `query_fb_marketing_api` has a parameter for `behaviors` to put behavior IDs. 

```{r simple_dib_ex, include=TRUE, warning=FALSE, message=FALSE}
behaviors_df <- get_fb_parameter_ids(type    = "behaviors",
                                     version = VERSION, 
                                     token   = TOKEN)

interests_df <- get_fb_parameter_ids(type    = "interests",
                                     version = VERSION, 
                                     token   = TOKEN)

job_titles_df <- get_fb_parameter_ids(type    = "job_titles",
                                      version = VERSION, 
                                      token   = TOKEN,
                                      q = "data")

behaviors_df %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%",
             height = "300px")
```

## Location Key <a name="param_locs"></a>

Users can be targeted by different types of [locations](https://developers.facebook.com/docs/marketing-api/audiences/reference/basic-targeting#location), including all users within a country, region (e.g., US state), city, neighborhood, etc. The `get_fb_parameter_ids` is used to obtain the location key for different places. The `type` parameter is used to define the type of location (e.g., `"country"`, `"region"`, etc.). 

In addition to `type`, the `country_code`, `region_id`, `key` and `q` parameters can be used to further refine searchers for locations. Providing an input for `country_code`, `region_id`, and `key` (e.g., city key), will search for locations within those larger locations. Providing an input to the `q` parameter limits the search by name. For smaller geographic regions, an input for `q` is required. 

| Location Type      | Radius Can be Specified | US Only |
| -----------------  | ----------------------  | ------- |
| country_group      | No                      | No      |
| country            | No
| region             |
| large_geo_area     |
| medium_geo_area    |
| small_geo_area     |
| metro_area         |
| city               |
| subcity            |
| neighborhood       |
| zip                |
| geo_market         |
| electoral_district |

```{r simple_loc_ex, include=TRUE, warning=FALSE, message=FALSE}
country_group_df <- get_fb_parameter_ids(type    = "country_group",
                                         version = VERSION, 
                                         token   = TOKEN)

country_df <- get_fb_parameter_ids(type    = "country",
                                   version = VERSION, 
                                   token   = TOKEN)

us_states_df <- get_fb_parameter_ids(type    = "region",
                                     version = VERSION, 
                                     token   = TOKEN,
                                     country_code = "US")

ny_key <- us_states_df %>% filter(name == "New York") %>% pull(key) 
ny_cities_df <- get_fb_parameter_ids(type    = "city",
                                     version = VERSION, 
                                     token   = TOKEN,
                                     region_id = ny_key,
                                     q = "New York")

ny_cities_df <- get_fb_parameter_ids(type    = "city",
                                     version = VERSION, 
                                     token   = TOKEN,
                                     region_id = ny_key,
                                     key = ny_cities_df %>% filter(name == "New York") %>% pull(key),
                                     q = "New York")



country_df %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%",
             height = "300px")
```

# Querying Data <a name="query_data"></a>

The `query_fb_marketing_api` function enables querying daily and monthly active users for specific locations and by specific types. Many parameters rely on IDs obtained from the `get_fb_parameter_ids` function. For example, `get_fb_parameter_ids` can be used to obtain the location key for New York City and the interest parameter ID for "Music (entertainment & media)"; these IDs can then be used in `query_fb_marketing_api` to obtain the number of Facebook users interested in music that live in New York City.

## Different Location Types <a name="query_data_loc"></a>

The number of daily and monthly active Facebook users can be queried (1) around a specific point (setting the latitude and longitude and the radius around this point), and (2) for a specific geographic (e.g., country, region, city, neighborhood, etc.). For small geographies, such as neighborhoods, a radius can also be set. 

### Radius around lat/lon <a name="query_data_loc_latlon"></a>

```{r simple_query_latlon_ex, include=TRUE, warning=FALSE, message=FALSE}

## All Facebook Users by Radius (Near NYC)
r5km_df <- query_fb_marketing_api(location_unit_type = "coordinates",
                                  lat_lon = c(40.712, -74.006),
                                  radius = 5,
                                  radius_unit = "kilometer",
                                  version            = VERSION, 
                                  creation_act       = CREATION_ACT, 
                                  token              = TOKEN)
```

### Location IDs - Country, State, District, City, Neighborhood, etc. <a name="query_data_loc_keys"></a>

We can also query using different location types, including countries, cities, etc. The `get_fb_parameter_ids()` function can be used to extract location keys for different location types; the location keys can then be used in the `query_fb_marketing_api()`. The below table indicates all the location types supported by the package. 

* __Location Type:__ This is specified (1) in the `type` parameter in the `get_fb_parameter_ids()` function and in the `location_unit_type` parameter in the `query_fb_marketing_api()` function
* __Radius Can be Specified:__ For these location types, a radius can optionally be specified; for example, to specify a location and it's surrounding area.
* __US Only:__ These location types can only be used for the US

| Location Type      | Radius Can be Specified | US Only | Example |
| -----------------  | ----------------------  | ------- | ------- |
| country_group      | No                      | No      | World Wide
| country            | No                      | No      | United States|
| region             | No                      | No      | New York |
| large_geo_area     | No                      | No      | Akkar, Lebanon |
| medium_geo_area    | No                      | No      | Henrico County, Virginia, USA |
| small_geo_area     | No                      | No      | El Rosario, Spain |
| city               | Yes                     | No      | New York City |
| subcity            | No                      | No      | Manhattan
| neighborhood       | No                      | No      | East Village, Manhattan |
| zip                | No                      | Yes     | 90210 |
| geo_market         | No                      | Yes     | New York| 
| electoral_district | No                      | Yes     | New York's 18th District, 2020 Census |

#### Country Groups

```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}

#### Country Group: World Wide
loc_df <- get_fb_parameter_ids(type = "country_group", 
                               version = VERSION, token = TOKEN)

query_fb_marketing_api(
  location_unit_type = "country_groups",
  location_keys      = loc_df %>% filter(name == "Worldwide") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Country

```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}
#### Country: United States
loc_df <- get_fb_parameter_ids(type = "country", 
                               version = VERSION, token = TOKEN)

us_df <- query_fb_marketing_api(
  location_unit_type = "countries",
  location_keys      = loc_df %>% filter(name == "United States") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Region
```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}

#### Region: New York (state)
region_df <- get_fb_parameter_ids(type = "region", country_code = "US", 
                                  version = VERSION, token = TOKEN)

ny_df <- query_fb_marketing_api(
  location_unit_type = "regions",
  location_keys      = region_df %>% filter(name == "New York") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Large Geographic Area

The Facebook Marketing [Targeting Search](https://developers.facebook.com/docs/marketing-api/audiences/reference/targeting-search) provides the following description about large geographic areas: _"Known commonly as a district or governate covering hundreds of square kilometers or more. Example: Akkar in Lebanon."_

```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}

#### Large Metro Area
loc_df <- get_fb_parameter_ids(type = "large_geo_area", 
                               country_code = "LB", 
                               q = "Akkar",
                               version = VERSION, token = TOKEN)

lma_df <- query_fb_marketing_api(
  location_unit_type = "large_geo_areas",
  location_keys      = loc_df %>% filter(name == "Akkar") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Medium Geographic Area

The Facebook Marketing [Targeting Search](https://developers.facebook.com/docs/marketing-api/audiences/reference/targeting-search) provides the following description about medium geographic areas: _"Known commonly as a county, covering more than one city. Example: Henrico county in the state of Virginia in United States."_

```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}

#### Large Metro Area
loc_df <- get_fb_parameter_ids(type = "medium_geo_area", 
                               country_code = "US", 
                               q = "Henrico",
                               version = VERSION, token = TOKEN)

mma_df <- query_fb_marketing_api(
  location_unit_type = "medium_geo_areas",
  location_keys      = loc_df %>% filter(name == "Henrico") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Small Geographic Area

The Facebook Marketing [Targeting Search](https://developers.facebook.com/docs/marketing-api/audiences/reference/targeting-search) provides the following description about small geographic areas: _"Known commonly as a residential area near a city or town. Example: El Rosario near Marbella in Spain."_

```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}

#### Large Metro Area
loc_df <- get_fb_parameter_ids(type = "small_geo_area", 
                               country_code = "ES", 
                               q = "El",
                               version = VERSION, token = TOKEN)

sma_df <- query_fb_marketing_api(
  location_unit_type = "small_geo_areas",
  location_keys      = loc_df %>% filter(name == "El Rosario") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### City
```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}
#### City: New York City
loc_df <- get_fb_parameter_ids(type = "city", 
                               region_id = region_df %>% filter(name == "New York") %>% pull(key),
                               q = "New York",
                               version = VERSION, token = TOKEN)

city_df <- query_fb_marketing_api(
  location_unit_type = "cities",
  location_keys      = loc_df %>% filter(name == "New York") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)

city_r_df <- query_fb_marketing_api(
  location_unit_type = "cities",
  location_keys      = loc_df %>% filter(name == "New York") %>% pull(key),
  radius             = 10,
  radius_unit        = "mile",
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Subcity
```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}
#### Subcity: Manhattan
loc_df <- get_fb_parameter_ids(type = "subcity", 
                               region_id = region_df %>% filter(name == "New York") %>% pull(key),
                               q = "Manhattan",
                               version = VERSION, token = TOKEN)

subcity_df <- query_fb_marketing_api(
  location_unit_type = "subcities",
  location_keys      = loc_df %>% filter(name == "Manhattan") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Neighborhood
```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}
loc_df <- get_fb_parameter_ids(type = "neighborhood", 
                               region_id = region_df %>% filter(name == "New York") %>% pull(key),
                               q = "East Village",
                               version = VERSION, token = TOKEN)

nbh_df <- query_fb_marketing_api(
  location_unit_type = "neighborhoods",
  location_keys      = loc_df %>% filter(name == "East Village, Manhattan") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Zip Code
```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}
## Zip codes can be dieectly entered as "US:[Zip Code]"
zip1_df <- query_fb_marketing_api(
  location_unit_type = "zips",
  location_keys      = "US:90210",
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)


## Zip codes can also be searched for using: "get_fb_parameter_ids"
loc_df <- get_fb_parameter_ids(type = "zip", 
                               q = "9", # Search using numbers
                               version = VERSION, token = TOKEN)

zip2_df <- query_fb_marketing_api(
  location_unit_type = "zips",
  location_keys      = loc_df %>% filter(name == "90210") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Geo Market (U.S. Designated Market Areas)

```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}
loc_df <- get_fb_parameter_ids(type = "geo_market", 
                               version = VERSION, token = TOKEN)

gm_df <- query_fb_marketing_api(
  location_unit_type = "geo_markets",
  location_keys      = loc_df %>% filter(name == "New York") %>% pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

#### Electoral Districts
```{r loc_country_group, include=TRUE, warning=FALSE, message=FALSE}
loc_df <- get_fb_parameter_ids(type = "electoral_district", 
                               q = "New York", 
                               version = VERSION, token = TOKEN)

ed_df <- query_fb_marketing_api(
  location_unit_type = "electoral_districts",
  location_keys      = loc_df %>% 
    filter(name == "New York's 18th District - 2020 Census") %>% 
    pull(key),
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)
```

## ID Options <a name="query_data_ids"></a>

### Options <a name="query_data_ids_options"></a>

```{r simple_query_params_ex, include=TRUE, warning=FALSE, message=FALSE}

# Likely commute to work in US
beh_comm_id <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
comm_us_df <- query_fb_marketing_api(location_unit_type = "countries",
                                     location_keys      = "US",
                                     behaviors          = beh_comm_id,
                                     version            = VERSION, 
                                     creation_act       = CREATION_ACT, 
                                     token              = TOKEN)

# Interested in music in US
int_music_id <- interests_df %>% filter(name == "Music (entertainment & media)") %>% pull(id)
music_us_df <- query_fb_marketing_api(location_unit_type = "countries",
                                      location_keys      = "US",
                                      interests          = int_music_id,
                                      version            = VERSION, 
                                      creation_act       = CREATION_ACT, 
                                      token              = TOKEN)

# Likely commute to work OR interested in music in US
comm_or_music_us_df <- query_fb_marketing_api(location_unit_type = "countries",
                                              location_keys      = "US",
                                              behaviors          = beh_comm_id,
                                              interests          = int_music_id,
                                              version            = VERSION, 
                                              creation_act       = CREATION_ACT, 
                                              token              = TOKEN)
```

### And and OR Categories <a name="query_data_ids_andor"></a>

When using multiple parameters (eg, behavior IDs), the function allows for specifying `and` and `or` condition; for example, identifying Facebook users that are commuters and/or are frequent travelers. Across parameters:

* __Vectors `c()`__ are used to specify OR conditions
* __Lists `list()`__ are used to specify AND conditions

However, the following parameters can only except one input (a list or vector is not allowed).
* `location_unit_type`
* `radius`
* `radius_unit`

#### Within parameter types <a name="query_data_ids_andor_within"></a>

```{r and_or_within, include=TRUE, warning=FALSE, message=FALSE}

beh_freqtrvl_id  <- behaviors_df %>% filter(name == "Frequent Travelers") %>% pull(id)
beh_comm_id      <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
beh_sb_id        <- behaviors_df %>% filter(name == "Small business owners") %>% pull(id)

# Commuters or Travelers
comm_or_trvl_df <- query_fb_marketing_api(location_unit_type = "countries",
                                          location_keys      = "US",
                                          behaviors          = c(beh_comm_id, beh_freqtrvl_id),
                                          version            = VERSION, 
                                          creation_act       = CREATION_ACT, 
                                          token              = TOKEN)

# Users who are (Commuters or Small Business Owners) and Travelers
comm_and_trvl_df <- query_fb_marketing_api(location_unit_type = "countries",
                                           location_keys      = "US",
                                           behaviors          = list(c(beh_comm_id,
                                                                       beh_sb_id), 
                                                                     beh_freqtrvl_id),
                                           version            = VERSION, 
                                           creation_act       = CREATION_ACT, 
                                           token              = TOKEN)
```

#### Flexible Targetting: Or and And <a name="query_data_ids_andor_flex"></a>

Flexible tagetting, using the `flex_target` parameter, allows for more complicated parameter specification---including AND conditions across parameter types (eg, behavior X and interest Y). The input for `flex_target` follows the following logic:

* `flex_target` uses named lists to specify the (1) parameter type and (2) parameter ID
* All parameters within the same list index are grouped using an OR condition
* All parameter separated across list indices are spearated by an AND condition

The below shows examples using dummy IDs

__Example 1: OR Condition__
The below shows an example setting an OR condition for interest ID 2 and behavior ID 2. Both interest:1 and behavior:2 are in the same list index, so are grouped using an OR condition (interests:1 OR behavior 2)
```
flex_param <- list("interests" = 1, "behaviors" = 2)
# flex_param[[1]]
```

__Example 2: AND Condition__
The below shows an example setting an AND condition for interest ID 2 and behavior ID 2. interest:1 and behavior:2 are separated across list indices, so are separated by an AND condition (interests:1 AND behavior:2)
```
flex_param <- list(list("interests" = 1), list("behaviors" = 2))
# flex_param[[1]] AND flex_param[[2]]
```

__Example 3: OR and AND Conditions__
The below shows a more complicated example, which grabs all users that meet EITHER interests:1 or behaviors:3 AND behaviors:2. Everything within `flex_param[[1]]` are grouped within OR conditions, but different indices (`flex_param[[1]]` and `flex_param[[2]]`) are separated by AND conditions.
```
flex_param <- list(list("interests" = 1, "behaviors" = 3), list("behaviors" = 2))
# flex_param[[1]] AND flex_param[[2]]
```

```{r and_or_across, include=TRUE, warning=FALSE, message=FALSE}

int_music_id <- interests_df %>% filter(name == "Music (entertainment & media)") %>% pull(id)
beh_comm_id  <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)

## OR CONDITION
comm_or_music_df <- query_fb_marketing_api(location_unit_type = "countries",
                                           location_keys      = "US",
                                           flex_target        = list("interests" = int_music_id,
                                                                     "behaviors" = beh_comm_id),
                                           version            = VERSION, 
                                           creation_act       = CREATION_ACT, 
                                           token              = TOKEN)

## AND CONDITION
comm_and_music_df <- query_fb_marketing_api(location_unit_type = "countries",
                                            location_keys      = "US",
                                            flex_target        = list(list("interests" = int_music_id),
                                                                      list("behaviors" = beh_comm_id)),
                                            version            = VERSION, 
                                            creation_act       = CREATION_ACT, 
                                            token              = TOKEN)

bind_rows(comm_or_music_df,
          comm_and_music_df) %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%",
             height = "100%")

```

### Exlcuding Categories <a name="query_data_ids_exclude"></a>

Many parameters come with an alternate input that starts with `excl_` to exclude types of users. For example, there are both `behaviors` and `interests` parameters, as well as `excl_behaviors` and `excl_interests` parameters. The below code shows an example querying users who likely commute to work and are not tagged as interested in music.

```{r exclude_ex, include=TRUE, warning=FALSE, message=FALSE}

# Likely commute to work BUT NOT interested in music in US
beh_comm_id  <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
int_music_id <- interests_df %>% filter(name == "Music (entertainment & media)") %>% pull(id)

comm_no_music_us_df <- query_fb_marketing_api(location_unit_type = "countries",
                                              location_keys      = "US",
                                              behaviors          = beh_comm_id,
                                              excl_interests     = int_music_id,
                                              version            = VERSION, 
                                              creation_act       = CREATION_ACT, 
                                              token              = TOKEN)
```


## Multiple Queries <a name="query_data_ids_multquery"></a>

The function allows making multiple queries within one function call. All parameters in the `map_param` function will be iterated as separate calls

### Simple Examples <a name="query_data_ids_multquery_simple"></a>

```{r vec_list_1, include=TRUE, warning=FALSE, message=FALSE}
## Number of Users in US or Mexico, as separate queries
df_out <- query_fb_marketing_api(location_unit_type = "countries",
                                 location_key       = map_param("US", "MX"),
                                 version            = VERSION, 
                                 creation_act       = CREATION_ACT, 
                                 token              = TOKEN)

df_out %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")

## Iterate across countries and across behaviors. Use `NA` for not filtering by behavior. The below call will give users for (1) all US, (2) all Mexico, (3) frequent travelers in US, and (4) frequenty travelers in Mexico.
df_out <- query_fb_marketing_api(location_unit_type = "countries",
                                 location_key       = map_param("US", "MX"),
                                 behaviors          = map_param(NA, beh_freqtrvl_id),
                                 version            = VERSION, 
                                 creation_act       = CREATION_ACT, 
                                 token              = TOKEN)

df_out %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")

## Separate query for number of users in US and Mexico and commuters and frequent travelers. Parameters not in
## map_param are applied across all queries. 
beh_comm_id      <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
beh_freqtrvl_id  <- behaviors_df %>% filter(name == "Frequent Travelers") %>% pull(id)
beh_sb_id        <- behaviors_df %>% filter(name == "Small business owners") %>% pull(id)
int_music_id     <- interests_df %>% filter(name == "Music (entertainment & media)") %>% pull(id)

df_out <- query_fb_marketing_api(location_unit_type = "countries",
                                 location_key       = map_param("US", "MX"),
                                 behaviors          = map_param(beh_comm_id, beh_freqtrvl_id),
                                 interests          = int_music_id,
                                 version            = VERSION, 
                                 creation_act       = CREATION_ACT, 
                                 token              = TOKEN)

df_out %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")
```

### And/Or Conditions <a name="query_data_ids_multquery_andor"></a>

And/or conditions work as before: vectors `c()` specify OR conditions, while lists `list()` specify and conditions

```{r vec_list_1_andor, include=TRUE, warning=FALSE, message=FALSE}

beh_freqtrvl_id  <- behaviors_df %>% filter(name == "Frequent Travelers") %>% pull(id)
beh_comm_id      <- behaviors_df %>% filter(name == "Commuters") %>% pull(id)
beh_sb_id        <- behaviors_df %>% filter(name == "Small business owners") %>% pull(id)

df_out <- query_fb_marketing_api(
  location_unit_type = "countries",
  location_key       = "US",
  behaviors          = map_param(
    # Commuters
    beh_comm_id, 
    
    # Frequent Travelers
    beh_freqtrvl_id, 
    
    # Commuters OR Frequent Travelers
    c(beh_comm_id, beh_freqtrvl_id),
    
    # Commuters AND Frequent Travelers
    list(beh_comm_id, beh_freqtrvl_id),
    
    # Commuters AND (Frequent Travelers OR Small Business Owners)
    list(beh_comm_id, c(beh_freqtrvl_id, beh_sb_id))
  ),
  
  version            = VERSION, 
  creation_act       = CREATION_ACT, 
  token              = TOKEN)

df_out %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")
```
